Increasing User Engagement in a Volunteer-Based Ephemeral Evolutionary Computation System

### 2017-02-16 2017-EUROPAR/Gamification/paper.tex
Added gamification section,
TO DO: Add Lucero’s Related Work

@@

\end{document}

>>>>

\begin{figure*}[t]
    \centering
        \includegraphics[width=5in]{img/login.png}
    \caption{Comparison of 30 runs of the 128 Bit OneMax problem. 
    Box-plot of the number of evaluations needed for solution, with a 2, 6 and 12 workers
    homogeneous configuration on the left side, and Heterogeneous configuration on the
    right side of each.
    }
    \label{fig:comp-onemax}
\end{figure*}

\section{Related Work}
\label{sec:experiments}

\section{Gamification.}
\label{sec:experiments}
A definition given by Huotari  \cite{huotari2012defining} is ``Gamification is
the process by which gaming concepts are brought to the real world tasks associated with
real people''. Gamification uses game design elements out of the domain of games 
with the objective of enhancing the user's experience, engagement, productivity, 
learning, among others. Deterding et al. proposes the following definition:
 ``Gamification” is the use of game design elements in non-game contexts'' 
 \cite{deterding2011gamification}.

\subsection{Techniques.}
Gamification techniques in a volunteer context seeks to persuade 
users to use their natural desire to compete, learn and socialize in 
given non-game context application \cite{deterding2011game, hamari2014does}.  
Some works give a form of reward to users, these include 
points \cite{sutter2010browse}, achievement badges or levels \cite{hamari2011framework}, 
the filling of a progress bar \cite{o2010get}, or providing the user with virtual currency.
By Making the rewards for  tasks achievements visible to other players or 
providing leader boards are ways of encouraging players to compete \cite{hickman2010total}. 
Competitio can also have problematic consequences, which can result in
negative conduct, low cooperation and collaboration, or disadvantaging certain player demographics
such as women \cite{kumar2013gamification}. Another techniques to gamification 
is to make existing tasks feel more like games \cite{deterding2010just}. 
Some techniques used in this approach include adding meaningful choice, 
onboarding with a tutorial, increasing challenge, and adding narrative \cite{mcgonigal2011reality}.

@@

\bibliographystyle{abbrv}
\bibliography{../../bib/biblio,../../bib/evospace-i,../../bib/volunteer,../../bib/geneura}
\end{document}
